---
title: "Carbonate Sputter Test"
date: '2020-12-10'
output:
  html_document:
    df_print: paged
---

Checking out data from carb sputter test on CFAMS121020. Precision was good, but accuracy not so much. Is this a 13C thing?

```{r}
library(tidyverse)
library(amstools)
library(here)

options(digits = 3)
```

```{r}
dfr <- read_csv(here("data/raw_carb_sputter.csv"))
df <- read_csv(here("data/carb_sputter.csv"))

dfs <- df %>% 
  select(wheel, wheel_pos, sample_name, norm_ratio, fm_corr, sig_fm_corr, del_13c, sig_13c)
dfs
```


```{r}
dfrs <- dfr %>% 
  select(wheel, wheel_pos, sample_name, le12c, le13c, he12c, 
         he13c, he13_12, he14_12, corr_14_12, d13c) %>% 
  mutate(he1312 = he13c/he12c,
         le1312 = le13c/le12c,
         hele13 = he13c/le13c,
         hele12 = he12c/le12c) %>% 
  group_by(wheel, wheel_pos, sample_name) %>% 
  summarise_all(mean) 
dfrs
```


Note difference in ratio of he13C to le13C between graphite and carbonate. A lot more "something" with mass 13 is making it through the accelerator. 12CH? Would this be an issue with USAMS?

```{r}
names(dfr)
dfr %>% 
  ggplot(aes(mst_num)) +
  geom_point(aes(y = le13c), size = 1) +
  geom_point(aes(y = he13c), size = 1, color = "blue") +
  scale_y_log10() +
  facet_wrap(~wheel)
```


```{r}
dfr %>% 
  ggplot(aes(mst_num)) +
  geom_point(aes(y = le12c), size = 1) +
  geom_point(aes(y = he12c), size = 1, color = "blue") +
  scale_y_log10() +
  facet_wrap(vars(wheel))
```


# Previous results

Get old raw data

Did we see similar performance during initial investigations?

```{r}
dfros <- dfro %>% 
  select(wheel, wheel_pos = Pos, sample_name = Sample.Name, le12c = le12C, le13c = le13C, he12c = he12C, 
         he13c = he13C, he13_12 = X13.12he, he14_12 = X14.12he, corr_14_12 = cor1412he) %>% 
  mutate(d13c = 1000 * (he13_12 - 1),
         he1312 = he13c/he12c,
         le1312 = le13c/le12c,
         hele13 = he13c/le13c,
         hele12 = he12c/le12c) %>% 
  group_by(wheel, wheel_pos, sample_name) %>% 
  summarise_all(mean) 
dfros
```

```{r}
names(dfros)
```


```{r}
names(dfrs)
```

```{r}
us042321 <- amstools::readResfile("/mnt/shared/USAMS/Results/USAMS042321R.txt") %>% 
  mungeResfile()

```

```{r}
ussum <- us042321 %>% 
  group_by(Pos) %>% 
  summarize(lec = mean(le12C))
```

