---
title: "USAMS112321 Carb Sputter"
author: "Brett Longworth"
date: "11/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(amstools)
```

Functions for adding consensus value and blank correction.

```{r}
add_consenus <- function(df) {
  # get rec_num
  db <- conNOSAMS()
  query <- glue::glue_sql("SELECT tp_num, rec_num
             FROM target
             WHERE tp_num IN ({tpnums*})",
             tpnums = df[['tp_num']],
             .con = db
  )
  
  recs <- odbc::dbSendQuery(db, query)
  recnums <- odbc::dbFetch(recs)
  odbc::dbClearResult(recs)
  df <- left_join(df, recnums)
  # get cons table
  std <- amstools::getStdTable()
  # join on rec_num
  df %>%  
    left_join(select(std, rec_num, fm_consensus), by = "rec_num") %>% 
    mutate(fm_consensus = case_when(rec_num == 101730 ~ 1.0398,
                                    rec_num == 72446 ~ 0.0013,
                                    TRUE ~ fm_consensus))
}

blank_cor_carb <- function(data, blanks = NULL, fmstd = 1.0398) {
  if (!is.null(blanks)) {
    data <- data %>% 
      mutate(sample_type = case_when(wheel_pos %in% blanks ~ "B",
                                     sample_type == "B" ~ "U",
                                     TRUE ~ sample_type ))
  }
  
  blanks <- data %>% 
    filter(sample_type == "B")
  
  data['sig_norm_ratio'] <- pmax(data['int_err'], data['ext_err'])
  
  meanblank <- mean(blanks$norm_ratio)
  
  # get blank error using SNICSer error floor
  blankerr <- amstools::blankErr(blanks$norm_ratio, blanks$sig_norm_ratio) # uses SNICSer error floor method
  # apply blank correction and propagate error
  data %>% 
    mutate(fm_corr = amstools::doLBC(norm_ratio, meanblank, fmstd),
           sig_fm_corr = amstools::doLBCerr(norm_ratio, meanblank, fmstd, sig_norm_ratio, blankerr)
    )
}
```

Load data, blank correct, add consensus values and comparison to consensus

```{r}
# consensus value for druffel coral
dcmean <- 0.9413

wheel <- getWheel("USAMS112621") %>% 
  blank_cor_carb(blanks = c(20,21)) %>% 
  add_consenus() %>% 
  mutate(fm_consensus = ifelse(rec_num == 21308, dcmean, fm_consensus),
         fm_diff = fm_corr - fm_consensus,
         sigma = amstools::sigma(fm_corr, fm_consensus, sig_fm_corr))

results <- wheel %>% 
  filter(wheel_pos %in% c(2:11, 13:21)) %>% 
  select(wheel_pos, rec_num, sample_name, norm_ratio, sig_norm_ratio, fm_corr, sig_fm_corr, fm_diff, sigma)
```

```{r}
knitr::kable(results)
```

```{r}
ggplot(results, aes(fm_corr, fm_diff)) +
  geom_point()
```



## Agreement with graphite

Agreement of Haiti core samples. Graphite samples were pretreated with HCl to leach 30% of the sample. HGIS samples not pretreated.

Load Simon's data and compare

```{r}
names <- results %>% 
  select(rec_num, sample_name)

graphite_results <- getRecOS(results$rec_num) %>% 
  filter(!is.na(reported)) %>% 
  select(rec_num, fm_corr = f_modern, sig_fm_corr = f_ext_error) %>% 
  mutate(method = "graphite") %>% 
  left_join(names, by = "rec_num")

combined_results <- results %>% 
  filter(str_starts(sample_name, "Pendleton")) %>% 
  mutate(method = "direct carb") %>% 
  select(sample_name, method, rec_num, fm_corr, sig_fm_corr) %>% 
  bind_rows(graphite_results) %>% 
  group_by(rec_num) %>% 
  mutate(fm_mean = mean(fm_corr),
         fm_diff = fm_corr - fm_mean) %>% 
  left_join(rename(names, Name = sample_name), by = "rec_num") %>% 
  ungroup()

combined_results %>% 
  select(sample_name, rec_num, method, fm_corr, sig_fm_corr) %>% 
  arrange(rec_num) %>% 
knitr::kable()
```

### Difference plot

```{r}
combined_results %>% 
  ggplot(aes(fm_corr, fm_diff, color = method, shape = method)) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  size = 1) +#,
                  #position = position_dodge2(width = 0.02)) +
  #ylim(-0.02, 0.02) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm") + theme_classic()
```

```{r}
combined_results %>% 
  ggplot(aes(rec_num, fm_corr, color = method, shape = method)) +
  geom_pointrange(aes(ymin = fm_corr - sig_fm_corr, 
                      ymax = fm_corr + sig_fm_corr),
                  size = .5,
                  position=position_dodge(width = .5)) +#,
                  #position = position_dodge2(width = 0.02)) +
  #ylim(-0.02, 0.02) +
  labs(title = "Haiti Core Graphite vs HGIS",
       y = "Fraction modern") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  facet_wrap("Name", scales = "free")
```

### Outliers

Need to get current

```{r}
combined_results %>% 
  filter(abs(fm_diff) > 0.02) %>% 
  select(sample_name, method, fm_corr, sig_fm_corr)
```